---
title: "Goals"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
source("./_site.R")
```

<!---From http://stackoverflow.com/questions/31753897/2-column-section-in-r-markdown:
Put in your css file or directly in rmarkdown--->
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
</style>

<font size="4">**What We Measure**

<font size="3">The Ocean Health Index measures the ability of oceans to sustainably provide benefits (called “goals” by the OHI) that are important to humans and biodiversity. The Ocean Health Index+ for South West England will assess the eight goals detailed [here](https://www.sustainable-seas.org/methods).   



<!--- Scroll down for a description of each goal as well as the model and data used to calculate the goal (blue text links to descriptions of the specific data used in the calculation of each goal. --->

<!--- TODO: link to supplement --->

</div>

----

```{r, eval=FALSE, child='goals.Rmd'}
```
